Joker: A Unified Interaction Model For Web Customization

### 2021-08-05 paper.tex
Fix typo in conclusion

In this paper, we presented a unified interaction model for web
customization. Our key idea is a spreadsheet formula language that
encompasses both extraction and augmentation tasks, along with a
programming-by-demonstration (PBD) interface that makes it easy for
end-users to program to create formulas. The main area of future work
involves making the formula language more accessible to end-users not
familiar with CSS selectors. Our ultimate goal is to enable anyone that
uses the web to customize websites in the course of their daily use in
an intuitive and flexible way.

>>>>

In this paper, we presented a unified interaction model for web
customization. Our key idea is a spreadsheet formula language that
encompasses both extraction and augmentation tasks, along with a
programming-by-demonstration (PBD) interface that makes it easy for
end-users to create formulas. The main area of future work involves
testing with more users and making the formula language more accessible
to end-users not familiar with CSS selectors. Our ultimate goal is to
enable anyone that uses the web to customize websites in the course of
their daily use in an intuitive and flexible way.
